Macroscopic Salt Rejection through Electrostatically Gated Porous Graphene

### 2019-01-09 paper/paper.tex
Add comment for delta definition

Next, we carried out the same experiments using the PG-covered PCTE
membrane (PG-PCTE), without electrostatic gating. The measured
diffusive flux values, $\boldsymbol{J}_{\mathrm{PG0}}$ (green bars in
\Fig{} \ref{fig:2}b), remain at the same order of magnitude compared
with those of bare PCTE membrane, suggesting that the mass transfer
resistance of PG is not significant, as the permeability is high. 
The diffusive transport resistance through graphene pores scales with $\sim$ 1/D while
for a PCTE pore, the scaling follows $\sim$ L/D$^2$ \cite{O_Hern_2014},
 D being the respective diameter and L the channel length. 
Taking into account that there are 10 graphene pores
per PCTE pore on average, the transport resistance ratio of R$_{graphene}$/R$_{PCTE}$ is roughly 1/30,
 indicating that the PCTE dominates the overall ion transport, which is in line 
 with the observed behavior.

@@

We further reveal the cation and anion transport pathways by looking
into their electrochemical potentials (\Fig{} \ref{fig:4}b). By
increasing $V_{\mathrm{G}}$, a more positive $\psi_{\mathrm{G}}$ on
graphene surface reduces the cation concentration at the pore edge due
to the electrostatic interactions, thereby increasing its
concentration gradient at the pore center. On the other hand, the
anion concentration near the pore edge increases exponentially, such
that the concentration gradient at the pore center becomes
small. (also see Supplementary \Fig{} S4). We also observe that
$\Delta \mu_{+}$ is dominated by the concentration, while
$\Delta \mu_{-}$ is much less than $\Delta \mu_{+}$ due to the balance
between the diffusion and drift potentials (see Supplementary \Fig{}
S5). The observations confirm the distinct ionic transport pathways
upon applying a positive $V_{\mathrm{G}}$: pore center for cations and
pore edge for anions. \Fig{} \ref{fig:4}c presents the calculated
\textit{z}-component of the cation and anion fluxes through the pore
at the graphene plane (z = 0), $\boldsymbol{J}_{z}$ ,as a function of
the normalized radius, $r/R_{\mathrm{G}}$ , where $r$ is the radial
coordinate and $R_{\mathrm{G}}$ is the pore radius, at different
$V_{\mathrm{G}}$ values. Note that $\boldsymbol{J}_{z}$ is negative
because the LCR is placed at z$<$0 in the simulation box. At
$V_{\mathrm{G}}$ = 0 (pure diffusion), the anion and cation flux
profiles are identical, with a higher flux near the pore edge, which
is expected, as the concentration gradient is higher. By gradually
increasing $V_{\mathrm{G}}$, both fluxes are reduced throughout the
pore, while the degree of reduction is more pronounced at the pore
edge for the cation, and at the pore center for the anion, following
the scenarios we discussed above. Accordingly, the integrated fluxes
across the pore, $|\boldsymbol{J}_{z}|$, are reduced with
$V_{\mathrm{G}}$ (\Fig{} \ref{fig:4}d). A total flux reduction of up
to 80\% is predicted. Another interesting finding here is that, by
increasing $V_{\mathrm{G}}$, the nanopore transport preferentially
allows cations over anions, or in other words, the anion flux is more
reduced with $V_{\mathrm{G}}$ (see \Fig{} \ref{fig:4}c), known as the
ion selectivity of graphene nanopore \cite{Rollings_2016}. In our setup, the imbalance between cation and anion
fluxes near the graphene nanopore is compensated by the EDL formation
at the counter-electrode in LCR, which maintains the electroneutrality
of the system. Notably, since atomically thin graphene samples are
used, the mechanism of salt rejection is clearly distinct from that in
capacitive deionization \cite{Li_2010}, where electrodes with large
surface area are required.

>>>>

Next, we carried out the same experiments using the PG-covered PCTE
membrane (PG-PCTE), without electrostatic gating. The measured
diffusive flux values, $\boldsymbol{J}_{\mathrm{PG0}}$ (green bars in
\Fig{} \ref{fig:2}b), remain at the same order of magnitude compared
with those of bare PCTE membrane, suggesting the transport resistance
of PCTE $R_{\mathrm{PCTE}}$, is dominant over that of PG,
$R_{\mathrm{G}}^{0}$. Using a simple circuit model, we estimate the
ratio $\delta$ between $R_{\mathrm{G}}^{0}$ and $R_{\mathrm{PG}}$,
such that $\delta = R_{\mathrm{PCTE}}/R_{\mathrm{G}}^{0}$, to be ~2,
which is in good agreement with the value derived from the
experimental data in \Fig{} \ref{fig:2}b (details see Supplementary Section SXX).
\todo[inline]{Make sure that the values used are correct.}

% The diffusive transport resistance through graphene pores scales with $\sim$ 1/D while
% for a PCTE pore, the scaling follows $\sim$ L/D$^2$ \cite{O_Hern_2014},
 % D being the respective diameter and L the channel length. 
% Taking into account that there are 10 graphene pores
% per PCTE pore on average, the transport resistance ratio of R$_{graphene}$/R$_{PCTE}$ is roughly 1/30,
 % indicating that the PCTE dominates the overall ion transport, which is in line 
 % with the observed behavior.

@@

We further reveal the cation and anion transport pathways by looking
into their electrochemical potentials (\Fig{} \ref{fig:4}b). By
increasing $V_{\mathrm{G}}$, a more positive $\psi_{\mathrm{G}}$ on
graphene surface reduces the cation concentration at the pore edge due
to the electrostatic interactions, thereby increasing its
concentration gradient at the pore center. On the other hand, the
anion concentration near the pore edge increases exponentially, such
that the concentration gradient at the pore center becomes
small. (also see Supplementary \Fig{} S4). We also observe that
$\Delta \mu_{+}$ is dominated by the concentration, while
$\Delta \mu_{-}$ is much less than $\Delta \mu_{+}$ due to the balance
between the diffusion and drift potentials (see Supplementary \Fig{}
S5). The observations confirm the distinct ionic transport pathways
upon applying a positive $V_{\mathrm{G}}$: pore center for cations and
pore edge for anions. \Fig{} \ref{fig:4}c presents the calculated
\textit{z}-component of the cation and anion fluxes through the pore
at the graphene plane (z = 0), $\boldsymbol{J}_{z}$ ,as a function of
the normalized radius, $r/R_{\mathrm{G}}$ , where $r$ is the radial
coordinate and $R_{\mathrm{G}}$ is the pore radius, at different
$V_{\mathrm{G}}$ values. Note that $\boldsymbol{J}_{z}$ is negative
because the LCR is placed at z$<$0 in the simulation box. At
$V_{\mathrm{G}}$ = 0 (pure diffusion), the anion and cation flux
profiles are identical, with a higher flux near the pore edge, which
is expected, as the concentration gradient is higher. By gradually
increasing $V_{\mathrm{G}}$, both fluxes are reduced throughout the
pore, while the degree of reduction is more pronounced at the pore
edge for the cation, and at the pore center for the anion, following
the scenarios we discussed above. Accordingly, the integrated fluxes
across the pore, $|\boldsymbol{J}_{z}|$, are reduced with
$V_{\mathrm{G}}$ (\Fig{} \ref{fig:4}d). A total flux reduction of up
to 80\% is predicted. Another interesting finding here is that, by
increasing $V_{\mathrm{G}}$, the nanopore transport preferentially
allows cations over anions, or in other words, the anion flux is more
reduced with $V_{\mathrm{G}}$ (see \Fig{} \ref{fig:4}c), known as the
ion selectivity of graphene nanopore \cite{Rollings_2016}. In our setup, the imbalance between cation and anion
fluxes near the graphene nanopore is compensated by the EDL formation
at the counter-electrode in LCR, which maintains the electroneutrality
of the system. Notably, since atomically thin graphene samples are
used, the mechanism of salt rejection is clearly distinct from that in
capacitive deionization \cite{Biesheuvel_2010}, where electrodes with large
surface area are required.
